---
title: | 
  | Assignment 4: Collaborating Together
  | Introduction to Applied Data Science
  | 2022-2023
author: |
  | Jerke Esmeijer
  | j.j.esmeijer@students.uu.nl
  | http://www.github.com/JerkeEs
date: April 2023
urlcolor: purple
linkcolor: purple
output: 
  pdf_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, error=TRUE)
```

```{r}
usethis::use_git_config(user.name = "JerkeEs",
user.email = "jerkie80@gmail.com")
```

## Assignment 4: Collaborating Together 

### Part 1: Contributing to another student's Github repository

In this assignment, you will create a Github repository, containing this document and the .pdf output, which analyzes a dataset individually using some of the tools we have developed. 

This time, make sure to not only put your name and student e-mail in your Rmarkdown header, but also your Github account, as I have done myself. 

However, you will also pair up with a class mate and contribute to each others' Github repository. Each student is supposed to contribute to another student's work by writing a short interpretation of 1 or 2 sentences at the designated place (this place is marked with **designated place**) in the other student's assignment. 

This interpretation will not be graded, but a Github shows the contributors to a certain repository. This way, we can see whether you have contributed to a repository of a class mate. 

**Question 1.1**: Fill in the __github username__ of the class mate to whose repository you have contributed. 

[I did not know we had to this assignment with someone else. I am a course repeater and due to a very busy schedule I couldn't make the tutorials, but I figured as long as I understand everything it is fine. Therefore I don't know any people from this course to do this part of the assignment. I don't know know if this is a problem, I hope not not. ]

### Part 2: Analyzing various linear models

In this part, we will summarize a dataset and create a couple of customized tables. Then, we will compare a couple of linear models to each other, and see which linear model fits the data the best, and yields the most interesting results.

We will use a dataset called `GrowthSW` from the `AER` package. This is a dataset containing 65 observations on 6 variables and investigates the determinants of economic growth. First, we will try to summarize the data using the `modelsummary` package. 

```{r, warning=FALSE, message=FALSE}
library(AER)
data(GrowthSW)
```

One of the variables in the dataset is `revolutions`, the number of revolutions, insurrections and coup d'etats in country $i$ from 1965 to 1995.

**Question 2.1**: Using the function `datasummary`, summarize the mean, median, sd, min, and max of the variables `growth`, and `rgdp60` between two groups: countries with `revolutions` equal to 0, and countries with more than 0 revolutions. Call this variable `treat`. Make sure to also write the resulting data set to memory. Hint: you can check some examples [here](https://vincentarelbundock.github.io/modelsummary/articles/datasummary.html#datasummary).

```{r}
library(modelsummary); library(tidyverse) 
```

```{r}
growthsw <- GrowthSW %>% mutate(treat = revolutions > 0)

summary_1 <- datasummary(growth + rgdp60 ~ treat* (mean + sd + median + min + max), data = growthsw)
```

**Designated place**: type one or two sentences describing this table of a fellow student below. For example, comment on the mean and median growth of both groups. Then stage, commit and push it to their github repository. 


### Part 3: Make a table summarizing reressions using modelsummary and kable

In question 2, we have seen that growth rates differ markedly between countries that experienced at least one revolution/episode of political stability and countries that did not. 

**Question 3.1**: Try to make this more precise this by performing a t-test on the variable growth according to the group variable you have created in the previous question. 

```{r}
t.test(growth ~ treat, data = growthsw)
```

**Question 3.2**: What is the $p$-value of the test, and what does that mean? Write down your answer below.

[Answer here]
The p-value is 0.06871. A large p value indicates the independent variable has a small or non existing effect on the dependent variable. A small p-value indicates there is an effect on the dependent variable. A p value of 0.06 is not precisely large, but it is not by any means small. With a significance level of 0.05 the 0 hypothesis would be accepted and there would be no evidence of relationship between the two variables.  

We can also control for other factors by including them in a linear model, for example:

$$
\text{growth}_i = \beta_0 + \beta_1 \cdot \text{treat}_i + \beta_2 \cdot \text{rgdp60}_i + \beta_3 \cdot \text{tradeshare}_i + \beta_4 \cdot \text{education}_i + \epsilon_i
$$

**Question 3.3**: What do you think the purpose of including the variable `rgdp60` is? Look at `?GrowthSW` to find out what the variables mean. 

[Answer here]
`rgdp60` is the value of GDP per capita in 1960. This could be useful to calculate the GDP growth, for countries with a higher GDP per capita usually generate higher growth rate numbers. 

We now want to estimate a stepwise model. Stepwise means that we first estimate a univariate regression $\text{growth}_i = \beta_0 + \beta_1 \cdot \text{treat}_i + \epsilon_i$, and in each subsequent model, we add one control variable. 

**Question 3.4**: Write four models, titled `model1`, `model2`, `model3`, `model4` (using the `lm` function) to memory. Hint: you can also use the `update` function to add variables to an already existing specification.

```{r}
model1 <- lm(growth ~ treat, data = growthsw)
model2 <- lm(growth ~ treat + rgdp60, data = growthsw)
model3 <- lm(growth ~ treat + rgdp60 + tradeshare, data = growthsw)
model4 <- lm(growth ~ treat + rgdp60 + tradeshare + education, data = growthsw)

```

Now, we put the models in a list, and see what `modelsummary` gives us:

```{r}
list(model1, model2, model3, model4) |>
  modelsummary(stars=T, 
              gof_map = c("nobs", "r.squared"))
```

# edit this to remove the statistics other than R-squared
# and N
**Question 3.5**: Edit the code chunk above to remove many statistics from the table, but keep only the number of observations $N$, and the $R^2$ statistic. 

**Question 3.6**: According to this analysis, what is the main driver of economic growth? Why?

[Answer here]
In the analysis you can see that the variable education has a p-value of < 0.001, which means that for this variable there is most evidence for a relation with growth. Also the R2 jumped up again after including education back in to the model, and a higher R2 means a higher percentage of the model can be explained through the included variables. So a higher R2 matched with the lowest p-value are a good sign for the argument that education is the main driver of economic growth.'

**Question 3.7**: In the code chunk below, edit the table such that the cells (including standard errors) corresponding to the variable `treat` have a red background and white text. Make sure to load the `kableExtra` library beforehand.

```{r}
library(kableExtra)

list <- list(model1, model2, model3, model4) |>
  modelsummary(stars=T, 
              gof_map = c("nobs", "r.squared"))

list(model1, model2, model3, model4) |>
  modelsummary(stars=T, 
              gof_map = c("nobs", "r.squared"),
              row_spec(color = "white", background = "#D7261E"))

# I can't get this part to run

```

**Question 3.8**: Write a piece of code that exports this table (without the formatting) to a Word document. 

```{r}
write.table(list, file = "C:/Users/jerki/Documents", sep = ",", quote = FALSE, row.names = F)

#There is the same error in this part as in the last part
```

End
------------------------
